Historical Soil Organic Carbon Budget

### 2020-06-16 SOCbudgetPaper/SOCbudget.tex
clean up file list for Paper Part

@@

Introduction text goes here. You can change the name of the section if
neccessary using
\texttt{\textbackslash{}introduction{[}modified\ heading{]}}. \newpage

@@

Following the tier 2 approach of the refinement of IPCC guidelines
vol.~4 (\citet{ipcc_2019_2019}), we estimate global land-use type
specific soil organic carbon (SOC) stocks for cropland and natural
vegetation on half-degree resolution from 1965 to 2010. We assume the
actual SOC state converges towards a stable steady state, that itself is
changing over time and space depending on biophysical, climatic and
agronomic conditions. Therefor we conduct the following three steps: (1)
Calculating annual land-use (sub-)type specific steady states and decay
rates for SOC stocks, (2) accounting for land conversion by transferring
SOC between land-use types and (3) updating SOC stocks based on the
previous stock, the steady state and the decay rate.

@@

In a simple first order kinetic approach the steady-state soil organic
carbon stocks \(SOC^{eq}\) are given by \begin{equation}
SOC^{eq} =\frac{C^{\textrm{in}}}{k}
\label{eq:inoutflow}
\end{equation} with \(C^{\textrm{in}}\) being carbon inputs to the soil
and \(k\) denoting the soil organic carbon decay rate. We use for our
calculations the steady-state method of the refinement of the IPCC
guidelines vol.~4 (\citet{ipcc_2019_2019}) for mineral soils, which
assume three soil carbon sub-pools (active, slow and passive) and
entangled dynamics between them. Annual carbon inflow to each sub-pool
(see @ref(sec:carboninputs)) and annual decay rates (see
@ref(sec:tier2)) of each sub-pool are still the key components to
determining steady-state SOC stocks.

@@

We account for different carbon input sources depending on the land-use
type (see table @ref(tab:datasourceinputs)). Following the IPCC
methodology carbon inputs are disaggregated into metabolic and
structural components depending on their lignin and nitrogen content
(see @ref(ipcc\_2019\_2019)). For each component the sum over all carbon
input sources is allocated to the respective SOC sub-pools via transfer
coefficients. This implies that not only the amount of carbon, but also
their structural composition is determining the effective inflow. Data
sources for all considered carbon inputs as well as for lignin and
nitrogen content can be found in table @ref(tab:datasourceinputs).

 \begin{table*}[h]
 \caption{Type and data sources for carbon inputs to different land-use types}
 \begin{tabular}{l l l l}
 \tophline
  land-use types   & source of carbon inputs & data source & nitrogen and lignin content \\
 \middlehline
 \multirow{3}{*}{Cropland} & residues & FAOSTAT, LPJmL4 [2, sec:residues] & default values given by [2]  \\
                            & dead below ground biomass of crops & FAOSTAT, LPJmL4 [2, sec:residues] & default values given by [2] \\
                            & manure & FAOSTAT, Isabelle [2, sec:manure] & default values given by [2] \\
                            \hline
  Natural vegetation        & annual litterfall & LPJmL4 [4]& \begin{minipage}[t]{0.28\columnwidth}\raggedright\strut Nitrogen and lignin content of tree compartments used in CENTURY [4] \strut \end{minipage}\tabularnewline
 \bottomhline
 \end{tabular}
 \label{tab:datasourceinputs}
 \belowtable{}
 \end{table*}

@@

@@

Agricultural management data is based on R library package moinput
(\citep{bodirsky_in_prep}), which compiles in its core country-specific
FAO production and cropland statistics (\citep{FAOSTAT}) to a
compherensive and constistent data suite. The data is prepared in 5 year
time steps from 1965 to 2010, which also restricts our analysis to this
time span. For all the following data, if not declared differently, we
interpolate values linearly between the time steps and hold it constant
before the first time step for a short spin-up phase from 1961 to 1965.

@@

Land-use patterns are based on the Land-Use Harmonization 2 (LUH2,
\citep{LUH2}) data set, which we aggregate from quarter degree to half
degree resolution. We disaggregate the five different cropland
subcategories (c3ann, c3per, c4ann, c4per, c3nfx) of LUH2 into our 17
crop groups, assuming relative shares for each gridcell based on the
country and year specific area shares of FAOSTAT data (\citep{FAOSTAT})
(see @ref(append:Table\_luh2fao2mag) for more details on the crop type
mapping). land-use transitions are calculated as net area differences of
the land-use data on half-degree.

@@

Crop residue production and management is based on a revised methodology
of (\citep{bodirsky2012}) and will be explained in key aspects again due
to its central role for soil carbon modelling. Starting from crop
production estimates of the harvested organs and their respective crop
area, we estimate above-ground (ag) and below-ground (bg) residual
biomass using yield-dependent harvest indices and shoot:root ratios. We
assume that all bg residues are recycled to the soil, whereas ag
residues can be burned or harvested for other purposes such as feeding
animals (\citep{weindl}), fuel or for material use.

@@

\subparagraph{Feed Demand}

@@

\subparagraph{Material and Fuel demand}

@@

\subparagraph{Recycled Residues}

@@

Using livestock production statistics as well as feed mix assumptions as
describted in (\citep{weindl}) we estimating country specific pasture
production. Following the same approach as for crop production we
disaggregate and calibrate half-degree pasture production pattern from
grass yields from LPJmL and pasture area and rangeland patterns ( (see
@ref(\#sec:landuse))) to derive half-degree pasture production patterns.

@@

To transform dry matter estimates into carbon, we compiled crop group
and plant part specific carbon to dry matter (c:dm) ratios (see
@ref(append:Table\_c2dm)) (\citet{Ma2018}).

@@

To disaggregate country level FAOSTAT livestock production values to
half-degree pattern, we use the following rule based assumptions which
were inspired by the approach of \citep{gilbert} and uses feed basket
assumptions based on a revised methodology of \citet{weindl}.

\subparagraph{Livestock Managament Intensities}

To account for different livestock management intensities, we
differentiate between extensive and an intensive systems assuming that
they have different requirements on production factors such as feed
availabiliy, access to markets and infrastructure (e.g.~roads, water).

\subparagraph{Dairy and ruminant Meat Production}

For extensive dairy and ruminant meat production we estimate, that
livestock is located rather immovable on pastures and rangeland. We use
the country-level pasture feed stuff shares within the feed baskets, to
split up pasture-fed, extensive from the rather intensive, crop-fed
livestock. Extensive production of dairy and ruminant meat is allocated
weighted by the pasture production values to all half-degree gridcell of
a country. On the other hand intensive dairy and ruminant meat
production is assumend to be located proportinal to crop production to
have short transport distances for feed stuff.

\subparagraph{Poultry, Egg and monogastric Meat Production}

For poultry, egg and monogastric meat production we use the per-capita
income of the country to divide into intensive and extensive production
systems. For low-income countries according to worldbank definitions
(\textless1000 USD/yr), we assume extensive production systems. We
located them according to built-up areas shares based on the idea that
these animals are held in households, subsistence or small-holder
farming systems with a high labour per animal ratio. Intensive
production is distributed within a country using the crop production
share, assuming that feed availability is the most driving factor for
livestock location.

\paragraph{Manure Excretion}

Manure production and management is based on a revised methodology of
(\citep{bodirsky2012}) and will be explained in key aspects again due to
its central role for soil carbon modelling. Based on the gridded
livestock distribution we calculate excretions by estimating the
nitrogen balance of the livestock system on the basis of comprehensive
livestock feed baskets (\citep{weindl}), assuming that all nitrogen in
protein feed intake, minus the nitrogen in the slaughter mass, is
excreted. Carbon in excreted manure is estimated by applying fixed C:N
ratios (given by \citep[(][]{ipcc_2019_2019}).

\paragraph{Manure Storage}

Depending on the feed system we assume manure to be handled in four
different ways: All manure orginated from pasture feed intake is
excreted directly to pastures and rangelands (pasture grazing) deducting
manure collected as fuel. Manure fuel shares are estimated using IPCC
default values (\citet{ippc_2006_2006}). Whereas for low-income
countries according to worldbank definitions (\textless1000 USD/yr), we
adopt a share of 25\% of crop residues in feed intake directly consumend
and excreted on crop fields (stubble grazing), we do not consider any
stubble grazing in high-income countries (\(>\,10000\,\tfrac{USD}{yr}\),
leaving middle-income countries with linearly interpolate shares
depending on their per-capita income. For all other feed items we assume
the manure to be stored in animal waste management systems associated to
animal houses.

\paragraph{Manure Recycling}

To estimate the carbon actually recycled to the soil, we account for
carbon losses during storage and recycling shares in different animal
waste management and grazing systems. Whereas we assume no losses for
pasture and stubble grazing, we consider all carbon lost for manure
collected as fuel. For manure stored in different animal waste
management system we compiled carbon loss rates partly depending on
nitrogen loss rates as specified in \citep{bodirsky2012} (see
@ref(append:Table\_clossAWMS))).

@@

Simple growing period calculations together with irrigation shares of
LUH2v2 are used (BB: you dont like d's, on't you) to estimate water
effects on decay rates.

@@

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-1} \caption{two column figure}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-2} \caption{two column figure}\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/figs_draft-3} \caption{two column figure}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/RegionPlot+Valid} \caption{two column figure}\label{fig:unnamed-chunk-9}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CShare_1965} \includegraphics[width=12cm]{images/maps/CShare_2010} \caption{two column figure}\label{fig:unnamed-chunk-10}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CIncrease_1965} \includegraphics[width=12cm]{images/maps/CIncrease_2010} \caption{two column figure}\label{fig:unnamed-chunk-11}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{images/maps/CShare_4ColorClimates} \caption{one column figure}\label{fig:unnamed-chunk-12}
\end{figure}
\newpage

@@

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}

@@

Within the last centuries the recognition of soil organic carbon (SOC)
has developed from being a major source of agricultural carbon emissions
towards a potentially large additional sink to offset other green house
gas emissions and thus mitigate climate change. Whereas the extent of
sink potential by SOC enhancement is highly debated (add refs), it is
largely agreed upon that the SOC pool itself is the biggest terrestrial
carbon pool, over topping the atmospheric and even more the biospheric
carbon pool multiple times. Even small changes in SOC drivers might lead
to substantial shifts in earth carbon cycled and influence the
atmospheric CO2 concentration (ref. permafrost melting). The specific
amount of carbon stored in the soil is uncertain though and estimates
ranging from 1500 to 2400 GtC for the first meter of the soil profile
(Bathjes, 1996).

Mapping the worlds SOC has been of great interest over the last decades
and led to an increased quality of SOC maps as well as a even better
understanding of factors driving magnitude, distribution and dynamics of
SOC pools. It is undisputed that natural properties like climatic,
biophysical and landscape characteristics play the most important role
in this regard. These factors can not be easily altered by human
intervention, leaving land cover, land use and land management changes
the most important factors for SOC dynamics till dawn of civilization .

Recent studies identified the SOC debt of anthropogenic source at around
116 GtC (Sanderman et al.), which compares to older estimates of around
60-130 GtC (Lal, 2006). Other studies have focus more closely on
spatially disaggregation SOC changes via advanced digital soil mapping
techniques (S-World; Stoorvogel 2, 2017) or better representation of
biogeochemcial processes within SOC dynamics (). Most of these studies
doing cutting edge research in their field, but seem to lack proper
representation of available information on land management.

On the other hand small-scale models (ref. Daycent, RothC, Ecosse,
C-Tool) are able to represent fairly well SOC dynamics on field-scale
driven by high quality management data on yield levels, fertilizer
inputs and various other on farming activities. Due to the lack of
proper, concise management data to feed these input demanding models on
larger extends, it seems still very complex to scale them up to a global
extent.

This study however wants to contribute filling the gap on impacts of
agricultural management like yield levels, residue recycling, manure
amendments, irrigation and tillage on SOC stocks of the worlds
croplands. It is doing so by combining work on agricultural management
data on global level with a robust but light weighted SOC model to
estimate SOC stocks and stock change factors as well as OC flow dynamics
within the agricultural system.

This is critically important since managing agricultural soil might be
one of the few setscrew for humans to \emph{naturally} combat climate
change (ref. to natural climate solutions). Other \emph{natural}
options, which might be summarized by restoring potential natural stocks
via renaturation of managed land, seem to be often limited due to
increased pressure on the land systems for feed, food and energy demand
of a growing and developing population on earth.

@@

Following the tier 2 approach of the refinement of IPCC guidelines
vol.~4 (\citet{ipcc_2019_2019}), we estimate global land-use type
specific soil organic carbon (SOC) stocks for cropland and natural
vegetation on half-degree resolution from 1965 to 2010. We assume the
actual SOC state converges towards a stable steady state, that itself is
changing over time and space depending on biophysical, climatic and
agronomic conditions. Therefore we conduct the following three steps
within each yearly timestep: (1) We calculate annual land-use (sub-)type
specific steady states and decay rates for SOC stocks, (2) We account
for land conversion by transferring SOC between land-use types and (3)
We estimate SOC stocks based on the stocks of the previous time period,
the steady state stocks and the decay rate.

@@

In a simple first order kinetic approach the steady-state soil organic
carbon stocks \(SOC^{eq}\) are given by \begin{equation}
SOC^{eq}_t =\frac{C^{\textrm{in}}_t}{k_t}
\label{eq:inoutflow}
\end{equation} with \(C^{\textrm{in}}\) being carbon inputs to the soil
and \(k\) denoting the soil organic carbon decay rate. We use for our
calculations the steady-state method of the refinement of the IPCC
guidelines vol.~4 (\citet{ipcc_2019_2019}) for mineral soils, which
assume three soil carbon sub-pools (active, slow and passive) and
entangled dynamics between them. Annual carbon inflow to each sub-pool
(see @ref(sec:carboninputs)) and annual decay rates (see
@ref(sec:tier2)) of each sub-pool are still the key components to
determining steady-state SOC stocks.

BB: I would include the t, also to show that the steady-state is
time-dependent.

@@

We account for different carbon input sources depending on the land-use
type (see table @ref(tab:datasourceinputs)). Name here the inputs, and
refer to the respective sections, dont just refer to the table.
Following the IPCC methodology carbon inputs are disaggregated into
metabolic and structural components depending on their lignin and
nitrogen content (see @ref(ipcc\_2019\_2019)). For each component the
sum over all carbon input sources is allocated to the respective SOC
sub-pools via transfer coefficients. This implies that not only the
amount of carbon, but also their structural composition is determining
the effective inflow. Data sources for all considered carbon inputs as
well as for lignin and nitrogen content can be found in table
@ref(tab:datasourceinputs).

 \begin{table*}[h]
 \caption{Type and data sources for carbon inputs to different land-use types }
 \begin{tabular}{l l l l}
 \tophline
  land-use types BB: table header should be bold   & source of carbon inputs & data source & nitrogen and lignin content \\
 \middlehline
 \multirow{3}{*}{Cropland} & residues & FAOSTAT, LPJmL4 [2, sec:residues] & default values given by [2]  \\
                            & dead below ground biomass of crops & FAOSTAT, LPJmL4 [2, sec:residues] & default values given by [2] \\
                            & manure & FAOSTAT, Isabelle [2, sec:manure] & default values given by [2] \\
                            \hline
  Natural vegetation        & annual litterfall & LPJmL4 [4]& \begin{minipage}[t]{0.28\columnwidth}\raggedright\strut Nitrogen and lignin content of tree compartments used in CENTURY [4] \strut \end{minipage}\tabularnewline
 \bottomhline
 \end{tabular}
 \label{tab:datasourceinputs}
 \belowtable{}
 \end{table*}

@@

This equation can also be reformulated to a massbalance equation as
follows:

\begin{equation}
SOC_{t} = SOC_{t-1} - k_{t} \cdot 1\unit{a} + C^{\textrm{in}}  \qquad \forall lut, sub, i.
\label{eq:steadystate}
\end{equation}

@@

Agricultural management data is estimated using the R library moinput
({[}cite git link{]}), which compiles country-specific FAO production
and cropland statistics (\citep{FAOSTAT}) to a comprehensive and
constistent data suite. BB: Isnt the whole calculation based on R
libraries? The data is prepared in 5 year time steps from 1965 to 2010,
which also restricts our analysis to this time span. For all the
following data, if not declared differently, we interpolate values
linearly between the time steps and hold it constant before the first
time step from 1961 to 1965. BB: too short for a spin-up, so dont use
this word. Maybe also just ignore this detail.

@@

Land-use patterns are based on the Land-Use Harmonization 2 (LUH2,
\citep{LUH2}) data set, which we aggregate from quarter degree to half
degree resolution. We disaggregate the five different cropland
subcategories (c3ann, c3per, c4ann, c4per, c3nfx) of LUH2 into our 17
crop groups, applying the relative shares for each gridcell based on the
country and year specific area harvested shares of FAOSTAT data
(\citep{FAOSTAT}) (see @ref(append:Table\_luh2fao2mag) for more details
on the crop type mapping). Land-use transitions are calculated as net
area differences of the land-use data on half-degree.

@@

Crop residue production and management is based on a revised methodology
of (\citep{bodirsky2012}) and will be explained in key aspects again due
to its central role for soil carbon modelling. Starting from crop
production estimates of the harvested organs and their respective crop
area, we estimate above-ground (ag) and below-ground (bg) residual
biomass using yield-dependent harvest indices and shoot:root ratios. We
assume that all bg residues are recycled to the soil, whereas ag
residues can be burned or harvested for other purposes such as feeding
animals (\citep{weindl}), fuel or for material use. BB: One new thing is
here that we use a doublecropping factor to account for lower harvest
indices of multicropping vs a very high single-cropped yield

@@

@@

@@

@@

Using livestock production statistics as well as feed mix assumptions as
describted in (\citep{weindl}) we estimating country specific pasture
production. Following the same approach as for crop production we
disaggregate and calibrate half-degree pasture production pattern from
grass yields from LPJmL and pasture area and rangeland patterns ( (see
@ref(\#sec:landuse))) to derive half-degree pasture production patterns.
BB: Oh, does that mean we assume that only the pasture grows that is
being eaten? Thats not too much, is it? Maybe ask Isabelle for a better
solution (e.g.~direct pasture yields from LPJmL). And then the ``pasture
production'' is just the part being removed by grazing. Does the IPCC
specifiy something in respect to pastures?

@@

To transform dry matter estimates into carbon, we compiled crop-group
and plant part specific carbon to dry matter (c:dm) ratios (see
@ref(append:Table\_c2dm)) (\citet{Ma2018}).

@@

To disaggregate country level FAOSTAT livestock production values to
half-degree pattern, we use the following rule based assumptions which
were inspired by the approach of \citep{gilbert} and uses feed basket
assumptions based on a revised methodology of \citet{weindl}. We
differentiate ruminant and monogastric systems, as well as extensive and
an intensive systems. For ruminants, we use the country-level shares of
gras within the feed baskets to split up pasture-fed, extensive systems
from the rather intensive crop-fed livestock. For extensive dairy and
ruminant meat production we estimate, that livestock is located in
proximity to pastures and rangelands and distribute manure excretion
proportional to pasture production of all half-degree gridcell of a
country. Intensive dairy and ruminant meat production is assumend to be
located proportinal to crop production to have short transport distances
for feed stuff.

BB: What does not become clear to me: Do the extensive cows only eat
pasture, and the intensive one only crops? Does that in the end mean we
just redistirbute grazed pasture to pastures and crop-based feed to
croplands proportional to production? Or is there more to it?

For poultry, egg and monogastric meat production we use the per-capita
income of the country to divide into intensive and extensive production
systems. For low-income countries according to worldbank definitions
(\textless1000 USD/yr), we assume extensive production systems. We
locate them according to built-up areas shares based on the idea that
these animals are held in households, subsistence or small-holder
farming systems with a high labour per animal ratio. Intensive
production is distributed within a country using the crop production
share, assuming that feed availability is the most driving factor for
livestock location.

\paragraph{Manure Excretion, Storage and Recycling}

Manure production and management is based on a revised methodology of
(\citep{bodirsky2012}) and will be explained in key aspects again due to
its central role for soil carbon modelling. Based on the gridded
livestock distribution we calculate excretions by estimating the
nitrogen balance of the livestock system on the basis of comprehensive
livestock feed baskets (\citep{weindl}), assuming that all nitrogen in
protein feed intake, minus the nitrogen in the slaughter mass, is
excreted. Carbon in excreted manure is estimated by applying fixed C:N
ratios (given by \citep[(][]{ipcc_2019_2019}). Depending on the feed
system we assume manure to be handled in four different ways: All manure
orginated from pasture feed intake is excreted directly to pastures and
rangelands (pasture grazing), deducting manure collected as fuel. Manure
fuel shares are estimated using IPCC default values
(\citet{ippc_2006_2006}). Whereas for low-income countries according to
worldbank definitions (\textless1000 USD/yr), we adopt a share of 25\%
of crop residues in feed intake directly consumend and excreted on crop
fields (stubble grazing), we do not consider any stubble grazing in
high-income countries (\(>\,10000\,\tfrac{USD}{yr}\), leaving
middle-income countries with linearly interpolate shares depending on
their per-capita income. For all other feed items we assume the manure
to be stored in animal waste management systems associated to animal
houses. To estimate the carbon actually recycled to the soil, we account
for carbon losses during storage and recycling shares in different
animal waste management and grazing systems. Whereas we assume no losses
for pasture and stubble grazing, we consider that the manure collected
as fuel is not recycled. For manure stored in different animal waste
management system we compiled carbon loss rates partly depending on the
nitrogen loss rates as specified in \citep{bodirsky2012} (see
@ref(append:Table\_clossAWMS))).

@@

BB: Where does the irrigated area come from? Simple growing period
calculations together with irrigation shares of LUH2v2 are used to
estimate water effects on decay rates.

@@

\begin{figure}
\includegraphics[width=17.78in]{../OldDataNotTracked/images/maps/CShare_1965} \includegraphics[width=17.78in]{../OldDataNotTracked/images/maps/CIncrease_1965} \caption{Test}\label{fig:unnamed-chunk-6}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{../OldDataNotTracked/images/figs_draft-1} \caption{two column figure}\label{fig:unnamed-chunk-7}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{../OldDataNotTracked/images/figs_draft-2} \caption{two column figure}\label{fig:unnamed-chunk-8}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{../OldDataNotTracked/images/figs_draft-3} \caption{two column figure}\label{fig:unnamed-chunk-9}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{../OldDataNotTracked/images/RegionPlot+Valid} \caption{two column figure}\label{fig:unnamed-chunk-10}
\end{figure}

\begin{figure}
\includegraphics[width=12cm]{../OldDataNotTracked/images/maps/CShare_4ColorClimates} \caption{one column figure}\label{fig:unnamed-chunk-11}
\end{figure}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{par}\NormalTok{(}\DataTypeTok{mar =} \KeywordTok{c}\NormalTok{(}\DecValTok{4}\NormalTok{, }\DecValTok{4}\NormalTok{, }\FloatTok{0.1}\NormalTok{, }\FloatTok{0.1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:table}SCF compared to potential natural state}
\centering
\begin{tabular}[t]{l|r|r|r|r}
\hline
  & tropical\_moist & tropical\_dry & temperate\_dry & temperate\_moist\\
\hline
1965 & 0.25 & 0.33 & 0.55 & 0.48\\
\hline
1970 & 0.29 & 0.36 & 0.56 & 0.50\\
\hline
1975 & 0.32 & 0.38 & 0.57 & 0.51\\
\hline
1980 & 0.34 & 0.38 & 0.56 & 0.53\\
\hline
1985 & 0.36 & 0.40 & 0.60 & 0.56\\
\hline
1990 & 0.38 & 0.42 & 0.63 & 0.58\\
\hline
1995 & 0.40 & 0.45 & 0.63 & 0.59\\
\hline
2000 & 0.42 & 0.47 & 0.64 & 0.60\\
\hline
2005 & 0.45 & 0.54 & 0.69 & 0.65\\
\hline
2010 & 0.50 & 0.58 & 0.73 & 0.67\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:table}SCF compared to actual natural state}
\centering
\begin{tabular}[t]{l|r|r|r|r}
\hline
  & tropical\_moist & tropical\_dry & temperate\_dry & temperate\_moist\\
\hline
1965 & 0.25 & 0.33 & 0.55 & 0.48\\
\hline
1970 & 0.29 & 0.36 & 0.56 & 0.50\\
\hline
1975 & 0.32 & 0.38 & 0.57 & 0.51\\
\hline
1980 & 0.34 & 0.38 & 0.56 & 0.53\\
\hline
1985 & 0.36 & 0.40 & 0.60 & 0.56\\
\hline
1990 & 0.38 & 0.42 & 0.63 & 0.58\\
\hline
1995 & 0.40 & 0.45 & 0.63 & 0.59\\
\hline
2000 & 0.42 & 0.47 & 0.64 & 0.60\\
\hline
2005 & 0.45 & 0.54 & 0.69 & 0.65\\
\hline
2010 & 0.50 & 0.58 & 0.74 & 0.68\\
\hline
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:table}Steady state SCF compared to actual natural state}
\centering
\begin{tabular}[t]{l|r|r|r|r}
\hline
  & tropical\_moist & tropical\_dry & temperate\_dry & temperate\_moist\\
\hline
1965 & 0.22 & 0.32 & 0.53 & 0.47\\
\hline
1970 & 0.24 & 0.46 & 0.52 & 0.53\\
\hline
1975 & 0.25 & 0.51 & 0.69 & 0.55\\
\hline
1980 & 0.26 & 0.45 & 0.68 & 0.63\\
\hline
1985 & 0.29 & 0.57 & 0.90 & 0.87\\
\hline
1990 & 0.31 & 0.60 & 0.90 & 0.87\\
\hline
1995 & 0.35 & 0.62 & 0.85 & 0.72\\
\hline
2000 & 0.37 & 0.67 & 0.85 & 0.78\\
\hline
2005 & 0.41 & 0.78 & 1.05 & 0.91\\
\hline
2010 & 0.47 & 0.83 & 1.30 & 0.95\\
\hline
\end{tabular}
\end{table}
\newpage

@@

Big points:

\begin{itemize}
\item
  SOC initialization is bad (Task: find a better representation)
\item
  natural land representation is lacking proper parametrization of
  natural input (n, lg content of litterfall) (--\textgreater{} ask
  Christop again)
\item
  boreal zone and dry regions are not well represented (maybe because of
  the bad parameterization of the soil model for natural soils)
\item
  As pointed out by Keel (2017), Smith (2019) the results might be
  highly sensitive to carbon input calculations more precisly to below
  and above ground residue carbon estimates derived from harvested
  quantities. It has been questioned, that below ground residues might
  increase with a fixed root:shot ratio (maybe specifically in high end
  farming systems (?)). Following this argumentation SOC results shown
  in this study might especially in high-yielding farming system (europe
  etc.) overestimate actual SOC stocks.
\item
  fertilizer interaction (--\textgreater{} ask LPJmLer again)
\item
  diaggregation of manure with urban area is leeding to a lot of
  displaced manure (?) that is cut off
\item
  mismatches between FAO/LUH
\end{itemize}

### 2020-06-16 SOCbudgetPaper/results.Rmd
clean up file list for Paper Part

# Content section with citations

See the [R Markdown docs for bibliographies and citations](http://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

Copernicus supports biblatex and a sample bibliography is in file `sample.bib`.
Read [], and [see ].

# Content section with R code chunks

```{r, echo = FALSE}
sum <- 1 + 41
```

You should always use `echo = FALSE` on R Markdown code blocks as they add formatting and styling not desired by Copernicus.
The hidden workflow results in `r sum`.

You can add verbatim code snippets without extra styles by using ` ``` ` without additional instructions.

```
sum <- 1 + 41
```

# Content section with list

If you want to insert a list, you must

- leave

- empty lines

- between each list item

>>>>

# Results

```{r table, echo = FALSE}

table <- readRDS("../ResultNotebooks/Output/SFC_climatezone.rds")
knitr::kable(table$naturalstate_table, "latex", digit=2, caption="SCF compared to potential natural state")
knitr::kable(table$actualstate_table,  "latex", digit=2, caption="SCF compared to actual natural state")
knitr::kable(table$steadystate_table,  "latex", digit=2, caption="Steady state SCF compared to actual natural state")

```
